KidsAIR wood stove grades and usage

### 2020-10-30 child_health_data_summary.Rmd
data cleaning and analysis updates

>>>>

```{r}
kids_at_home_log <- read_rds(paste0(file_path, "Output/kids_at_home_log.rds"))

at_home_summary <- kids_at_home_log %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
  arrange(area, home, child_id_num, sampling_day, sample_time) %>% 
  group_by(area, home, child_id_num) %>% 
  mutate(total_n = n(),
         time_home = sum(at_home, na.rm = TRUE),
         at_home_percent = time_home/total_n*100) %>% 
  ungroup() %>% 
  filter(!is.na(treatment_assigned)) %>% 
  group_by(area, treatment_assigned) %>% 
  summarize(mean_at_home = mean(at_home_percent, na.rm = TRUE),
            sd_at_home = sd(at_home_percent, na.rm = TRUE),
            min_at_home = min(at_home_percent, na.rm = TRUE),
            median_at_home = median(at_home_percent, na.rm = TRUE),
            max_at_home = max(at_home_percent, na.rm = TRUE))
at_home_summary

at_home_n <- kids_at_home_log %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
  filter(!is.na(treatment_assigned)) %>% 
  filter(!is.na(at_home)) %>% 
  distinct(area, home, child_id_num, .keep_all = TRUE) %>% 
  count(area, treatment_assigned)
at_home_n
```

### 2020-10-30 main_analysis_initial.Rmd
data cleaning and analysis updates

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_final_data, by = c("area", "home", "child_id_num")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_overall, 
         person_time_at_risk_total, lrti_incidence, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, pm_sample_interval,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5) %>% 
  rename(treatment = newtx,
         lrti_events = lrti_events_overall,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di = if_else(lrti_events == 0, 0, 1)) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  filter(area == "NN") %>% # Change area filter as necessary
  distinct(area, home, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  group_by(treatment) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment, new_var) %>% 
    mutate(n = n(),
         percent = round(n()/treatment_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(treatment, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_treatment("gender_parent")
char_funct_total("race_parent")
char_funct_treatment("race_parent")
char_funct_total("education_3level")
char_funct_treatment("education_3level")
char_funct_total("income_3level")
char_funct_treatment("income_3level")
char_funct_total("home_floors_2level")
char_funct_treatment("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_treatment("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_treatment("home_pets_2level")
char_funct_total("home_pets_3level")
char_funct_treatment("home_pets_3level")
char_funct_total("residents_smoke")
char_funct_treatment("residents_smoke")
char_funct_total("residents_smoke_inside")
char_funct_treatment("residents_smoke_inside")
char_funct_total("stove_age_3level")
char_funct_treatment("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_treatment("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_treatment("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_treatment("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_treatment("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_treatment("burn_level_3level")
char_funct_total("ruca_code")
char_funct_treatment("ruca_code")
char_funct_total("ruca_code_2")
char_funct_treatment("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_treatment("ruca_code_3")
```

@@

# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  filter(area == "NN") %>% # Change area filter as necessary
  distinct(area, home, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(!is.na(new_var)) %>% 
  select(treatment, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(!is.na(new_var)) %>% 
  select(treatment, home, new_var) %>% 
  group_by(treatment) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_total("residents_under_five")
num_funct_treatment("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_treatment("home_bedrooms")
num_funct_total("pm_mean_sampling_period")
num_funct_treatment("pm_mean_sampling_period")
num_funct_total("pm_sample_interval")
num_funct_treatment("pm_sample_interval")
num_funct_total("moisture_closest")
num_funct_treatment("moisture_closest")
num_funct_total("temp_indoor_max")
num_funct_treatment("temp_indoor_max")
num_funct_total("rh_indoor_max")
num_funct_treatment("rh_indoor_max")
num_funct_total("mean_temp")
num_funct_treatment("mean_temp")
num_funct_total("amb_pm_24hr")
num_funct_treatment("amb_pm_24hr")
num_funct_total("sums_events_sampling_period_2.5")
num_funct_treatment("sums_events_sampling_period_2.5")
num_funct_total("sums_events_sampling_period_5")
num_funct_treatment("sums_events_sampling_period_5")
num_funct_total("sums_events_sampling_period_7.5")
num_funct_treatment("sums_events_sampling_period_7.5")

>>>>

# Merge dataset with blinded treatments and final LRTI data, select analysis variables
kids_analysis_data_1obs_per_child <- health_exposure_data_sampling_day %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  mutate(child_age = fct_collapse(age_child_nov,
                                  "< 1" = "Less than 1",
                                  "1+" = c(1, 2, 3, 4))) %>% 
  left_join(treatments_masked, by = "home") %>% 
  arrange(area, home, child_id_num, winter_id, age_child_nov) %>% 
  right_join(lrti_final_data, by = c("area", "home", "child_id_num")) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  dplyr::select(area, home, cohort, child_id_num, child_age, lrti_events_overall, 
         person_time_at_risk_total, lrti_incidence, newtx, treatment_assigned,
         amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti,
         gender_parent, hispanic_parent, race_parent, education_3level, income_3level,
         home_floors_2level, home_year_built_2level, home_pets_2level, home_pets,
         stove_age_3level, chimney_clean_3level, wood_collect_method_2level,
         wood_collect_2level, stove_grade_3level, burn_level_3level, ruca_code,
         ruca_code_2, ruca_code_3, residents_smoke, residents_smoke_inside,
         residents_under_five, home_bedrooms, pm_mean_sampling_period, 
         pm_sample_interval, pm_at_home_sampling_period,
         moisture_closest, temp_indoor_max, rh_indoor_max, sums_events_sampling_period_2.5,
         sums_events_sampling_period_5, sums_events_sampling_period_7.5,
         home_act_smoking_sum, home_act_windows_sum, home_act_sweep_sum, home_act_door_sum) %>% 
  rename(treatment = newtx,
         lrti_events = lrti_events_overall,
         person_time_at_risk = person_time_at_risk_total) %>% 
  mutate(log_person_time_at_risk = log(person_time_at_risk)) %>% 
  mutate(lrti_events_di = if_else(lrti_events == 0, 0, 1)) %>% 
  mutate(treatment = factor(treatment,
                            levels = c("Blackfoot", "Dearborn", "Smith")),
         treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education")))

@@

# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
    #select(-treatment_assigned, -treatment_actual) %>% 
  #left_join(treatments_masked, by = "home") %>%
  #rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  #filter(area == "NN") %>% # Change area filter as necessary
  distinct(area, home, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  group_by(treatment_assigned) %>% 
  mutate(treatment_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
    mutate(n = n(),
         percent = round(n()/treatment_n*100)) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_treatment("gender_parent")
char_funct_total("race_parent")
char_funct_treatment("race_parent")
char_funct_total("education_3level")
char_funct_treatment("education_3level")
char_funct_total("income_3level")
char_funct_treatment("income_3level")
char_funct_total("home_floors_2level")
char_funct_treatment("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_treatment("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_treatment("home_pets_2level")
char_funct_total("home_pets_3level")
char_funct_treatment("home_pets_3level")
char_funct_total("residents_smoke")
char_funct_treatment("residents_smoke")
char_funct_total("residents_smoke_inside")
char_funct_treatment("residents_smoke_inside")
char_funct_total("stove_age_3level")
char_funct_treatment("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_treatment("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_treatment("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_treatment("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_treatment("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_treatment("burn_level_3level")
char_funct_total("ruca_code")
char_funct_treatment("ruca_code")
char_funct_total("ruca_code_2")
char_funct_treatment("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_treatment("ruca_code_3")
char_funct_total("home_act_smoking_sum")
char_funct_treatment("home_act_smoking_sum")
char_funct_total("home_act_windows_sum")
char_funct_treatment("home_act_windows_sum")
char_funct_total("home_act_sweep_sum")
char_funct_treatment("home_act_sweep_sum")
char_funct_total("home_act_door_sum")
char_funct_treatment("home_act_door_sum")
```

@@

# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  mutate(treatment_assigned = factor(treatment_assigned,
                                     levels = c("Placebo", "Filter", "Education"))) %>% 
  #select(-treatment_assigned, -treatment_actual) %>% 
  #left_join(treatments_masked, by = "home") %>%
  #rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  #filter(area == "AK") %>% # Change area filter as necessary
  distinct(area, home, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(!is.na(new_var)) %>% 
  select(treatment_assigned, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(!is.na(new_var)) %>% 
  select(treatment_assigned, home, new_var) %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

num_funct_total("residents_under_five")
num_funct_treatment("residents_under_five")
num_funct_total("home_bedrooms")
num_funct_treatment("home_bedrooms")
num_funct_total("pm_mean_sampling_period")
num_funct_treatment("pm_mean_sampling_period")
num_funct_total("pm_sample_interval")
num_funct_treatment("pm_sample_interval")
num_funct_total("moisture_closest")
num_funct_treatment("moisture_closest")
num_funct_total("temp_indoor_max")
num_funct_treatment("temp_indoor_max")
num_funct_total("rh_indoor_max")
num_funct_treatment("rh_indoor_max")
num_funct_total("mean_temp")
num_funct_treatment("mean_temp")
num_funct_total("amb_pm_24hr")
num_funct_treatment("amb_pm_24hr")
num_funct_total("sums_events_sampling_period_2.5")
num_funct_treatment("sums_events_sampling_period_2.5")
num_funct_total("sums_events_sampling_period_5")
num_funct_treatment("sums_events_sampling_period_5")
num_funct_total("sums_events_sampling_period_7.5")
num_funct_treatment("sums_events_sampling_period_7.5")
num_funct_total("home_act_smoking_sum")
num_funct_treatment("home_act_smoking_sum")
num_funct_total("home_act_windows_sum")
num_funct_treatment("home_act_windows_sum")
num_funct_total("home_act_sweep_sum")
num_funct_treatment("home_act_sweep_sum")
num_funct_total("home_act_door_sum")
num_funct_treatment("home_act_door_sum")
num_funct_total("home_act_incense_sum")
num_funct_treatment("home_act_candle_sum")

### 2020-10-30 main_analysis_secondary_models.Rmd
data cleaning and analysis updates

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))
```

@@

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
itt_education_tidy <- results_function(itt_education_results, "ITT + education")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_home_tidy <- results_function(itt_home_results, "ITT home only")
itt_no_age_tidy <- results_function(itt_no_age_results, "ITT - age")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

itt_results_combined <- rbind(itt_tidy, itt_income_tidy, itt_education_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_home_tidy,
                              itt_no_age_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT home only",
                                   "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "Systolic BP ITT models") +
  labs(y = "LRTI events per child-week at risk \n compared to placebo treatment") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = .8, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates
```

>>>>

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  dplyr::select(area, home, child_id_num, at_home, at_home_location)
```

@@

itt_smoking_results <- glmer.nb(lrti_events ~ treatment_assigned + child_age + (1 | home:cohort:area) + 
                        home_act_smoking_sum + 
                        offset(log_person_time_at_risk), data = analysis_data)

itt_windows_results <- glmer.nb(lrti_events ~ treatment_assigned + child_age + (1 | home:cohort:area) + 
                        home_act_windows_sum + 
                        offset(log_person_time_at_risk), data = analysis_data)

itt_door_results <- glmer.nb(lrti_events ~ treatment_assigned + child_age + (1 | home:cohort:area) + 
                        home_act_door_sum + 
                        offset(log_person_time_at_risk), data = analysis_data)

itt_sweep_results <- glmer.nb(lrti_events ~ treatment_assigned + child_age + (1 | home:cohort:area) + 
                        home_act_sweep_sum + 
                        offset(log_person_time_at_risk), data = analysis_data)

@@

# Run results through function, save, combine for plotting
itt_tidy <- results_function(itt_results, "ITT Primary")
itt_income_tidy <- results_function(itt_income_results, "ITT + income")
itt_education_tidy <- results_function(itt_education_results, "ITT + education")
itt_smoke_tidy <- results_function(itt_smoke_results, "ITT + smoke hx")
itt_burn_level_tidy <- results_function(itt_burn_level_results, "ITT + burn level")
itt_smoking_tidy <- results_function(itt_smoking_results, "ITT + smoke act")
itt_windows_tidy <- results_function(itt_windows_results, "ITT + window act")
itt_door_tidy <- results_function(itt_door_results, "ITT + door act")
itt_sweep_tidy <- results_function(itt_sweep_results, "ITT + sweep act")
itt_home_tidy <- results_function(itt_home_results, "ITT home only")
itt_no_age_tidy <- results_function(itt_no_age_results, "ITT - age")
itt_outlier_tidy <- results_function(itt_outlier_results, "ITT outlier")

itt_results_combined <- rbind(itt_tidy, itt_income_tidy, itt_education_tidy, 
                              itt_smoke_tidy, itt_burn_level_tidy, itt_smoking_tidy,
                              itt_windows_tidy, itt_door_tidy, itt_sweep_tidy,
                              itt_home_tidy, itt_no_age_tidy, itt_outlier_tidy)

# Plot results
itt_plot_estimates <- itt_results_combined %>%
  mutate(model = factor(model,
                        levels = c("ITT Primary", "ITT + income", "ITT + education",
                                   "ITT + smoke hx", "ITT + burn level", "ITT + smoke act",
                                   "ITT + window act", "ITT + door act", "ITT + sweep act",
                                   "ITT home only", "ITT - age", "ITT outlier"))) %>% 
  ggplot(aes(group = term, shape = term)) +
  geom_point(aes(x=model, y=estimate), 
             position = position_dodge(width = 0.5), size = 4) +
  #scale_shape_manual(values = c(15, 16, 17, 18, 13, 9)) +
  geom_errorbar(aes(x=model, ymin=conf.low, ymax=conf.high), 
             position = position_dodge(width = 0.5), size = 1.2, width = 0.5) +
  geom_hline(yintercept = 0) +
  theme_bw() +  
  #ggtitle(label = "Systolic BP ITT models") +
  labs(y = "LRTI events per child-week at risk \n compared to placebo treatment") +
  labs(x = "", group = "", shape = "") +
  theme(title = element_text(size = 16), 
          axis.text.x = element_text(size = 16, colour = "black", angle = 25,
                                     hjust = 1, vjust = .8),
          axis.text.y = element_text(size = 16, colour = "black"),
          axis.title.y = element_text(size = 16,
                                      margin = margin(t = 0, r = 20, b = 0, l = 0)),
          axis.line.x = element_line(colour = "black", size = 1.2), 
          axis.line.y = element_line(colour = "black", size = 1.2), 
          axis.ticks = element_blank(), 
          panel.border = element_blank(), 
          panel.grid = element_blank(),
          legend.position = "top",
          legend.text = element_text(size = 14, colour = "black")) 
itt_plot_estimates
```

### 2020-10-30 stove_grade_usage_cleaning.Rmd
data cleaning and analysis updates

>>>>

# Load, format, and KW compliance report
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

##### WMT #####
# Load data
kw_report_wmt <- read_csv(paste0(file_path, "Input/WMT/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         area = "WMT") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

# Save as RDS
write_rds(kw_report_wmt, paste0(file_path, "Output/kw_report_wmt.rds"))

##### NN #####
# Load data
kw_report_nn <- read_csv(paste0(file_path, "Input/NN/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         area = "NN") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

# Save as RDS
write_rds(kw_report_nn, paste0(file_path, "Output/kw_report_nn.rds"))

##### AK #####
# Load data
kw_report_ak <- read_csv(paste0(file_path, "Input/AK/filtrete_report.csv"), 
                                  na = c("NULL", "")) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         home = as.factor(Home),
         kw_date = ymd(ChangeDate),
         kw_hours = as.numeric(KWHours),
         kw_notes = as.character(Notes),
         hours_possible = as.numeric(Hours),
         kw_expected = as.numeric(Expected),
         kw_perc_expected = as.numeric(PercExp),
         area = "AK") %>% 
  dplyr::select(area, home, home_winter_id, kw_date, kw_hours, kw_notes, 
         hours_possible, kw_expected, kw_perc_expected) %>% 
  #filter(!is.na(kw_hours)) %>% 
  ungroup() %>% 
  arrange(home_winter_id, kw_date)

# Save as RDS
write_rds(kw_report_ak, paste0(file_path, "Output/kw_report_ak.rds"))
```

# Join KW report data from different areas
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

kw_report_wmt <- read_rds(paste0(file_path, "Output/kw_report_wmt.rds"))
kw_report_nn <- read_rds(paste0(file_path, "Output/kw_report_nn.rds"))
kw_report_ak <- read_rds(paste0(file_path, "Output/kw_report_ak.rds"))

kids_kw_report <- rbind(kw_report_wmt, kw_report_nn, kw_report_ak) %>% 
  dplyr::select(-home) %>% 
  ungroup() %>% 
  arrange(area, home_winter_id, kw_date)

write_rds(kids_kw_report, paste0(file_path, "Output/kids_kw_report.rds"))
```

# Clean up all KW report data
```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")
kids_kw_report <- read_rds(paste0(file_path, "Output/kids_kw_report.rds"))
kids_linked_ids <- read_rds(paste0(file_path, "Output/kids_linked_ids_final.rds"))
treatments_masked <- read_csv(paste0(file_path, "Input/KidsAIRrnd_masked.csv"), na = "NULL") %>% 
  mutate(home = gsub(" ", "", x = home),
         home = gsub("_", "", x = home))

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  arrange(area, home_winter_id)

summary(kids_kw_report_clean)

kw_summary <- kids_kw_report_clean %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  #filter(area == "WMT") %>% 
  #group_by(treatment_assigned) %>% 
  summarize(mean(kw_perc_expected),
            sd(kw_perc_expected),
            n(),
            min(kw_perc_expected),
            median(kw_perc_expected),
            max(kw_perc_expected))
kw_summary

write_rds(kids_kw_report_clean, paste0(file_path, "Output/kids_kw_report_clean.rds"))
```
